Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-17 ICML-submission/from-weak-separability-to-strong-separability.tex
Small fixes

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
\begin{align*}
p(x)
& = p(x_1, x_2, \dots, x_d) \\
& = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
\end{align*}
where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$, denoted
by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
Following the terminology of~\cite{Klivans-Servedio-2008},
the \emph{norm of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
$$
It is easy see that this is indeed a norm, since we can interpret it as the
Euclidean norm of the vector of the coefficients of the polynomial.

>>>>

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
\begin{align*}
p(x)
& = p(x_1, x_2, \dots, x_d) \\
& = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
\end{align*}
where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
\alpha_d}$'s are real coefficients. The \emph{degree} of a polynomial $p$,
denoted by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots +
\alpha_d$ for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is
non-zero. Following the terminology of~\citet{Klivans-Servedio-2008}, the
\emph{norm of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
$$
It is easy see that this is indeed a norm, since we can interpret it as the
Euclidean norm of the vector of the coefficients of the polynomial.
